Make any stupid plot you want

### 2020-12-07 draft/sections/math.tex
coherency maybe

As illustrated by figure~\ref{fig:fiberbundle}, the vertical lines $F$ are the range of possible temperature values embedded in the total space $E$. The base space $K$ of the fiber bundle describes the connectivity of the points in $E$; in figure~\ref{fig:fiberbundle} the connectivty of the timeseries is encoded in the line representation of $K$.

@@

\begin{figure}
    \includegraphics{figures/sections/math/k_qspace.png}
    \label{fig:kquotient}
\end{figure}

$K$ is the quotient space of $E$, meaning it is the set of equivalence classes of elements $p$ in of $E$ defined via the map $\pi: E \rightarrow K$ that sends each point $p \in E$ to its equivalence class in $[p] \in K$ \cite{QuotientSpaceTopology2020,QuotientSpaceTopology2020}. As shown in figure~\ref{fig:kquotient}, the fibers $F$ divide $E$ into smaller spaces consisisting of $F$ and an open set neighborhood around $F$. This subdivision is projected down to the toplology $\Tau_k$

\begin{equation}
\tau_K = {U\subseteqq K: {p \in E: [p] \in U}\in \Tau_E}
\end{equation}

@@

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}

@@

\subsubsection{Channels}
Acts on different parts of F, types means measurement groups , can be broken out so tau(E_{u} in E)
Tau can preserves the measurement type properties (group scales)

>>>>

As illustrated by figure~\ref{fig:fiberbundle}, the vertical lines $F$ are the range of possible temperature values embedded in the total space $E$. The base space $K$ of the fiber bundle describes the connectivity of the points in $E$; in figure~\ref{fig:fiberbundle} the connectivity of the timeseries is encoded in the line representation of $K$.

@@

\begin{figure}[ht]
    \includegraphics[width=0.4\linewidth]{figures/sections/math/k_qspace.png}
    \label{fig:kquotient}
\end{figure}

$K$ is the quotient space of $E$, meaning it is the set of equivalence classes of elements $p$ in of $E$ defined via the map $\pi: E \rightarrow K$ that sends each point $p \in E$ to its equivalence class in $[p] \in K$ \cite{QuotientSpaceTopology2020,QuotientSpaceTopology2020}. As shown in figure~\ref{fig:kquotient}, the fibers $F$ divide $E$ into smaller spaces consisisting of $F$ and an open set neighborhood around $F$. This subdivision is projected down to the toplology $\tau_k$

\begin{equation}
\tau_K = \{U\subseteqq K: \{p \in E: [p] \in U\}\in \tau_E\}
\end{equation}

@@

\begin{figure}[ht]
    \label{fig:k_data}
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
    %% add box around neighboring P and Map
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}

We use $K$ to encode the connectivity of the points $p$, such as the ones in figure~\ref{fig:k_data} that only store temperature data. In a timeseries, the temperature $p$ at timme $t$ is dependent on the value at $p_{t-1}$ and $\p_{t+1}$ is dependent on the value in $p_t$; this connectivity is expressed as a one dimensional $K$ where $K$ is the number line. In the case of the map, every point $p$ is dependent on its nearest neighbors on the plane, and one way to express this is by encoding $K$ as a plane. $K$ does not know the time or latitude or longitude of the point - those are metadata variables potentially encoded in $p$ because they are ways of describing the connectivity rather than the connectivity itself. The mapping $sigma: K \rightarrow E$ provides the binding between the key on $K$ and the value $p$ in $E$ \cite{munznerChDataAbstraction}

@@

\subsubsection{Channels}
Acts on different parts of F, types means measurement groups , can be broken out so 
%%tau(E_{u} in E)
Tau can preserves the measurement type properties (group scales)
